---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### The `MultiDoE` package

The `MultiDoE` package can be used to construct multi-stratum experimental designs (for any number of strata) that optimize up to six statistical criteria simultaneously. To solve such optimization problems, the innovative MS-Opt and MS-TPLS algorithms are implemented. The former relies on a local search procedure to find a locally optimal experimental design. More precisely, it is an extension of the Coordinate-Exchange (CE) algorithm that allows both the search of experimental designs for any type of nested multi-stratum experiment and the optimization of multiple criteria simultaneously. The latter, by embedding MS-Opt in a Two-Phase Local Search framework, is able to generate a good Pareto front approximation for the optimization problem under study. The package provides different ways to choose the final optimal experimental design among those belonging to the Pareto front.

In what follows, we report a practical example.

### The protein extraction experiment
In this experiment, a split-plot design is used. The final aim is to investigate the effect of five factors on protein extraction. More precisely, a mixture containing two valuable proteins, among other components, is considered after fermentation and purification processes. 

The experiment is intended to separate the two proteins from the mixture, and the responses were the yields and purities of the two proteins. The factors are: $x_1$, the feed position for the inflow of a mixture, which is hard to set; $x_2$ the feed flow rate; $x_3$ the gas flow rate; $x_4$ the concentration of the first protein; $x_5$, the concentration of the second protein. Three levels are used for each factor. The split-plot design was set up as follows: one whole-plot factor, four subplot factors, twenty-one whole plots of size two, and 42 runs.

Let use the package for simultaneously optmize more than one criterion.

First step is to upload the package.
```{r setup}
library(multiDoE)
```

It is time to initialize the main arguments for defining the experimental design.

```{r }
set.seed(13)
options(digits = 15)

facts <- list(1, 2:5)
units <- list(21, 2)
levels <- 3
etas <- list(1)
criteria <- c('Id', 'Ds')
model <- "quadratic"
```

`facts` is a list of vectors representing the distribution of factors across strata. Each item in the list represents a stratum and the first item is the highest stratum of the multi-stratum structure of the experiment. Within the vectors, experimental factors are indicated by progressive integer from 1 (the first factor of the highest stratum) to the total number of experimental factors (the last factor of the lowest stratum). Blocking factors are differently denoted by empty vectors.

`units` is a list whose $i$-th element, $n_i$, is the number of experimental units within each unit at the previous stratum ($i-1$).

`levels` is the number of available levels for each experimental factor.

`etas` is used to specify the ratios of error variance between subsequent strata, starting from the highest strata.

`criteria` is a list specifying the criteria to be optimized among I-, Id-, D-, A-, Ds, and As-optimality.

`model` is a string which indicates the type of model, among main effects only ("main"), interaction ("interaction") and full quadratic ("quadratic").

Now, we need to declare the main arguments for the MS-TPLS algorithms in order to get the final Pareto Front.

```{r}
iters <- 5 * length(criteria)
restarts <- 20
restInit <- 2
```

`model` is an integer indicating the number of iterations of the MS-TPLS algorithm. In this case, we set the iteration as 5 times the number of criteria.

`restarts` defines the number of times the MS-Opt procedure is altogether called within each iteration of the MS-TPLS algorithm.

`restInit` determines how many of the iterations of MS-Opt should be used for each criterion in the first step of the MS-TPLS algorithm.

`restarts` and `restInit`may be tuned.

We now simultaneously minimize Id- and Ds-criteria.

```{r}
tpls <- runTPLS(facts,units, criteria, model, iters, 
                "Restarts", restarts, 
                "RestInit", restInit)
```
